LME-MPM applied to quasi-brittle fracture.

### 2020-05-21 2020_EFM_MPM_Eigensoftening.tex
Pequeños cambios

\section{Conclusions}
\label{sec:4}
Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
\cite{Zhang_EE_2020}, we have proposed two addition improvements which
solves the shortcomings presented in the original concept. First by
bring to the \acrshort{mpm} framework the concept of eigensoftening,
which allow to consider gradual failure process of each material
point. This concept can be compared with cohesive law in the context
of cohesive fracture. Furthermore, more elaborated damage curves can
be designed to describe the failure process in sophisticated
materials. In this direction, an interesting future improvement of the
algorithm would be the ability to simulate of crack patterns in
composite material such carbon fiber. This leads a challenging
research topic. Secondly, \acrshort{lme} is employed to remove from
the solution those wiggles due to inaccuracies in the stress
integration. This interpolation technique could help to improve the
results in fracture propagation by adapting it thorough the
deformation gradient. \textit{A priori} this will enhance the already
impressive localisation properties of eigensoftening and eigenerosion
algorithms.

>>>>

\section{Conclusions}
\label{sec:4}
Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
\cite{Zhang_EE_2020}, we have proposed two addition improvements which
solves the shortcomings presented in the original concept. First by
bring to the \acrshort{mpm} framework the concept of eigensoftening,
which allow to consider gradual failure process of each material
point. This concept can be compared with a cohesive law in the context
of cohesive fracture. Furthermore, more elaborated damage curves can
be designed to describe the failure process in more sophisticated
materials. In this direction, an interesting future improvement of the
algorithm would be the ability to simulate of crack patterns in
composite material such carbon fiber. This leads a challenging
research topic. Secondly, \acrshort{lme} is employed to remove from
the solution those wiggles due to inaccuracies in the stress
integration. This interpolation technique could help to improve
results in fracture propagation by adapting it thorough the
deformation gradient. \textit{A priori} this will enhance the already
impressive localisation properties of eigensoftening and eigenerosion
algorithms.
